### 2025-07-31 Revision/response.tex

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig/attribute_legend.pdf}
	\includegraphics[width=0.495\linewidth]{fig/attribute_85.pdf}
	\includegraphics[width=0.47\linewidth]{fig/attribute_71.pdf}
	\caption{Different Platforms (AF)}
	\label{fig:attribute-cross-platform}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig/range_legend.pdf}
	\includegraphics[width=0.495\linewidth]{fig/range_85.pdf}
	\includegraphics[width=0.47\linewidth]{fig/range_71.pdf}
	\caption{Different Platforms (RF)}
	\label{fig:range-cross-platform}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%% R6 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{In Table 1, please clarify which methods are disk-based, and which methods are memory-based.
			For disk-based methods, it is also meaningful to report the cost breakdown (e.g., in terms of I/O time and CPU time).}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. Currently, except for Filtered-DiskANN, other hybrid query methods are memory-based, so we added the characteristic of whether to support disk for each algorithm in Table \ref{tab:compair_1}, which corresponds to Table 1 in the original paper.
\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/recall_latency_all.pdf}
	\caption{Performance Comparison of SSD-Based and In-Memory Execution of FilteredDiskANN}
	\label{fig:recall-latency}
\end{figure}

@@

 To analyze the cost breakdown of disk-based methods in greater detail, we also compared the search performance difference of Filtered-DiskANN on memory and SSD using real data sets. 
We conducted additional experiments on the YT-Audio-Real dataset, comparing three variants of DiskANN.
(1) SSD-based Filtered-DiskANN (original disk-based method);
(2) FilteredVamana (memory-based method);
(3) StitchedVamana (memory-based method).
We have run all experiments with 32 search threads for fair comparison. Figure~\ref{fig:recall-latency} shows the mean latency (log-scale, left y-axis) and I/O vs CPU proportion (right y-axis) across different Recall\@10 levels:

%\begin{itemize}
%	\item SSD-based FilteredDiskANN (original disk-based method)
%	\item FilteredVamana (memory-based method)
%	\item StitchedVamana (memory-based method)
%\end{itemize}

Latency-Recall Tradeoff:
As expected, SSD-based Filtered-DiskANN exhibits significantly higher latency than in-memory methods, especially at higher recall levels. When Recall@10 reaches 0.96, its latency increases super-linearly to over 100 ms.

Cost Breakdown of Filtered-DiskANN:The I/O proportion consistently dominates, maintaining 80\%–85\% of the total latency even at different recall levels.
The CPU proportion remains low (10–15\%), indicating that I/O is the major bottleneck in disk-based search pipelines.
This clearly shows that improving disk read efficiency or reducing I/O volume is critical for performance optimization.

In-memory Methods:
FilteredVamana achieves a good balance, staying under 30 ms while achieving Recall@10 > 0.97.
While StitchedVamana achieves extremely low latency (sub-5 ms) due to its stitched multi-label index structure, its fixed edge connectivity may limit effectiveness under highly uncorrelated label distributions. Nevertheless, it consistently supports 90\%+ Recall@10 across diverse datasets, as shown in our evaluations.

\textbf{Note: }Due to space limitations and the fact that only one method supports disk-based execution, we did not include the above experiments and analysis in the revised paper.

@@

\textcolor{blue}{
	ACORN demonstrates average overall performance. Among its variants, ACORN-1 shows significant advantages in indexing speed on 100M-scale datasets, but suffers from high memory consumption and delivers only moderate performance.}

\textcolor{blue}{
	Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects, which indicates that its strategy of loading data pages on-demand is unsuitable for performance-demanding scenarios."}
%下面放那个优劣势表

%%%%%%%%%%%%%%%%%%%%%% R10 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Clearer guidelines in the Discussion to the extend of recommendations on which system/algo to use for what dataset characteristics.}
	\end{metarevision}
}

\noindent
\textbf{Response:} Thank you very much for your valuable suggestions. Your advice is very insightful. In the recommendation section of our paper, we have added a clearer summary table of the algorithms to help readers choose the appropriate algorithm based on their application scenarios, as shown in Table~\ref{tab:algorithm_recommendation}. \textbf{(Please see Section 5.1, highlighted in blue in the revised manuscript.)}

\textcolor{blue}{"Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table 1. "}

@@

\section*{Response to Review 2}
\setcounter{weakness}{0}

%%%%%%%%%%%%%%%%%%%%%% W1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{observation}
		\textit{In the experimental study, datasets did not originate from the real applications for hybrid queries.
			Regarding the datasets for AF-NN search (Msong, Audio, SIFT1M, GIST1M, GloVe, Enron),
			the attributes were generated synthetically but not real.
			Regarding the datasets for RF-NN search (Deep, YT-Audio, WIT), the data point ID was used as attribute;
			however, it is not meaningful to issue range query on data point ID.
			In order to match with the introduction, the authors are recommended to
			include a real dataset from e-commerce platform with both vectors and attributes.
		}
	\end{observation}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We fully understand your concern regarding our use of synthetic or less meaningful attributes in the hybrid query experimental setup.

Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction. We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_images\_18K and MEP-3M datasets. However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
Specifically, the ecommerce\_product\_images\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets. On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT (Also called WIT-Real) and YouTube-Audio (Also YT-Audio-Real) datasets, which are widely employed in existing hybrid querying algorithm research. These datasets feature real attribute information and have been broadly accepted by the community as standard benchmarks for evaluating hybrid query performance.  For more details, please refer to our response to Meta R3.

For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly. \textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}

@@

\noindent
\textbf{Response:} 
Thank you for your suggestion. We clarify in Table ~\ref{tab:compair_1} which methods support disk-based execution. Since only FilteredDiskANN supports disk-based execution, we conduct additional experiments to analyze its performance and report a detailed cost breakdown (I/O vs. CPU). Figure~\ref{fig:recall-latency} shows that I/O consistently dominates total latency (accounting for 80–85\%) and becomes the primary bottleneck at high recall levels. We also compare it with two in-memory baselines—FilteredVamana and StitchedVamana—to highlight their efficiency and trade-offs. Due to space constraints and the limited relevance to other methods, we exclude this analysis from the revised paper and provide it here for completeness.

We have already provided a detailed response to this issue in our reply to Meta R5. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% W4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{observation}
		\textit{The authors have reported the peak memory usage of index construction only.
			They are also recommended to report the peak memory usage of query processing.}
	\end{observation}
}

\noindent
\textbf{Response:} 
We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component. We are deeply aware of this shortcoming, so we provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. For more details, please refer to our response Meta R6.

@@

%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:} 
%Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
Thank you for pointing this out. The original reference [49](now [50] in our latest version), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms. We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques. We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version. To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}

### 2025-07-31 Revision/response.tex

For attribute filtering, by incorporating the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes, we have revised the "Single-Attribute Index Construction and Single-Attribute Query" experiments and amended the manuscript accordingly. It is also worth noting that in Section 4.2.2, under the "Single-Attribute Index Construction and Single-Attribute Query" subsection, we have removed two previous datasets (Audio and GloVe) due to space constraints. The Audio dataset was removed because its smaller scale offered limited reference value. The GloVe dataset is similar in scale to SIFT1M, while LID is similar to GIST1M. \textbf{(Please see Section 4.2.1, and the "Single-Attribute Index Construction and Single-Attribute Query" subsection in Section 4.2.2,  highlighted in blue in the revised manuscript.).}

In fact, we have conducted experiments to verify that the choice between synthetic and real-world attributes has a minimal impact on the performance of algorithms. For more details, please refer to our response to Review 1 W1.

For range filtering, we have also included the YT-Audio-Real and WIT-Real datasets with their respective real-world attributes in our experiments. For more details, please refer to our response to Meta R3.

Regarding your review comment, we did indeed try to find suitable e-commerce datasets to better align with the application scenarios mentioned in the introduction. We investigated some publicly available e-commerce datasets, such as ecommerce\_product\_image\\-s\_18K and MEP-3M datasets. However, we found that neither of these datasets fully met our requirements for conducting hybrid querying experiments.
Specifically, the ecommerce\_product\_image\\-s\_18K dataset was too small to effectively evaluate the performance and scalability of hybrid querying algorithms under large-scale datasets. On the other hand, while the MEP-3M dataset was larger, it did not directly provide image data that could be encoded into vectors, and we were unable to find suitable fields for vectorization.
As we were unable to locate an ideal e-commerce dataset that simultaneously contained sufficient scale of both vectors and structured attributes, we ultimately decided to continue using the WIT and YouTube-Audio datasets, which are widely employed in existing hybrid querying algorithm research. These datasets feature real attribute information and have been broadly accepted by the community as standard benchmarks for evaluating hybrid query performance. We believe that despite not being directly from e-commerce platforms, their data characteristics and complexity are sufficient to support our comprehensive evaluation and in-depth analysis of hybrid querying algorithms.

@@

\noindent
\textbf{Response:} 
We believe your suggestion is very reasonable, and the experiment on search peak memory is indeed an important component. We provide the search peak memory usage of each algorithm in the time and space overhead section and carefully analyze the reasons. For more details, please refer to our response Meta R6.

%We have made a detailed response to this issue in our reply to Meta R6. Please refer to that response for more information.

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The authors have cited an experimental paper [49],
			but have not discussed about the main difference between their paper and [49].}
	\end{detailed}
}

\noindent
\textbf{Response:} 
%Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.
Thank you for pointing this out. The original reference [49] ([45] in the revised manuscript), provides a comprehensive review and evaluation of graph-based approximate nearest neighbor (ANN) search algorithms, whereas our work is the first to establish a benchmark specifically for hybrid query algorithms. We initially cited this reference in the experimental setup section to adopt its proposed evaluation metrics, as hybrid queries are fundamentally built upon ANN techniques. We acknowledge that the distinction between our work and the cited paper was not clearly articulated in the early version. To address this, we have revised the introduction to clarify the difference and added citations to several experimental studies from the ANN literature. \textbf{(Please see Section 1.1, highlighted in blue in the revised manuscript.)}

### 2025-07-31 Revision/response.tex

\textbf{Regarding index partitioning and merging:}

For partitioning and merging, only Filtered-DiskANN, which supports disk storage, builds indices separately and then merges them. However, the algorithms we focused on and evaluated in this study (with the exception of Filtered-DiskANN) are all designed and implemented based on in-memory index construction. Therefore, for the vast majority of algorithms, index partitioning and merging are not involved, which differs from the design considerations of DiskANN.

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, Faiss, Puck, Filtered-DiskANN, and Milvus support quantization.
Quantization serves to reduce memory usage during queries by sacrificing query accuracy. Given that most of the graph-based algorithms involved in this paper (with the exception of Filtered-DiskANN) do not support quantization, we do not enable quantization in our experiments for a fair comparison. Therefore, the reported index construction time does not include quantization time.
